---
title: "plots"
author: "Meng Yuan"
date: "2022/4/29"
output: html_document
---

Total movie ratings per genre
```{r}
genre_rating <- split_edx%>%
  group_by(genres) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```

Ratings distribution
```{r}
vec_ratings <- as.vector(edx$rating)
unique(vec_ratings) 
##  [1] 5.0 3.0 2.0 4.5 3.5 4.0 1.0 1.5 2.5 0.5
vec_ratings <- vec_ratings[vec_ratings != 0]
vec_ratings <- factor(vec_ratings)
qplot(vec_ratings) +
  ggtitle("Ratings' Distribution")
```
The distribution of each user’s ratings for movies. This shows the users bias
```{r} 
edx %>% count(userId) %>% 
  ggplot(aes(n)) + 
  geom_histogram(bins = 30, color = "black") + 
  scale_x_log10() + 
  ggtitle("Users")
```
Some movies are rated more often than others.Below is their distribution. This explores movie biases.
```{r} 
edx %>% 
  count(movieId) %>% 
  ggplot(aes(n)) + 
  geom_histogram(bins = 30, color = "black") + 
  scale_x_log10() + 
  ggtitle("Movies")
```
 Genres popularity per year. Here we tackle the issue of temporal evolution of users taste over different popular genre.
```{r} 
genres_popularity <- split_edx %>%
  na.omit() %>% # omit missing values
  select(movieId, year, genres) %>% # select columns we are interested in
  mutate(genres = as.factor(genres)) %>% # turn genres in factors
  group_by(year, genres) %>% # group data by year and genre
  summarise(number = n()) %>% # count
  complete(year = full_seq(year, 1), genres, fill = list(number = 0)) # add missing years/genres
# Genres vs year; 4 genres are chosen for readability: animation, sci-fi, war and western movies.
genres_popularity %>%
  filter(year > 1930) %>%
  filter(genres %in% c("War", "Sci-Fi", "Animation", "Western")) %>%
  ggplot(aes(x = year, y = number)) +
  geom_line(aes(color=genres)) +
  scale_fill_brewer(palette = "Paired") 
```
 Rating vs release year. Here, a general trend of movie viewers and their rating habits can be explored.    
```{r} 
edx %>% group_by(year) %>%
  summarize(rating = mean(rating)) %>%
  ggplot(aes(year, rating)) +
  geom_point() +
  geom_smooth()
## `geom_smooth()` using method = 'loess' and formula 'y ~ x'
```